The Early Arrival of WASP-4\lowercase{b}

### 2018-12-08 paper/ms.tex
update broadband mag paragraph

\tablecomments{
  (A) From TESS lightcurves (\S~\ref{sec:measurement}).
  (B) \citet{hoyer_tramos_2013}.
  (C) \citet{triaud_spin-orbit_2010}.
  (D) From HARPS spectra \citep{doyle_accurate_2013}.
  (E) \citet{stassun_accurate_2017}.
  (F) From functions of stellar, transit or RV parameters as discussed in text.
  (G) Gaia DR2.
  (H) \citet{stassun_TIC_2018}.
}

@@

\citet{stassun_accurate_2017} found the bolometric flux from
broad-band photometry.  Combining the implied angular radius with the
{\it Gaia} DR2 parallax, and adjusting for the parallax offset
\citep{stassun_evidence_2018}, we obtain the stellar radius.  For the
stellar mass, we started with the $a/R_\star$ value found by
\citet{hoyer_tramos_2013} from 26 ground-based transits.  The implied
semi-major axis and stellar density follow \citep{seager_unique_2003}.
Combining the density and radius gives the stellar mass.  We get the
planet radius using our measured $R_{\rm p}/R_\star$.  Finally, for
the planet mass we use the observed RV semi-amplitude and inclination
angle from the transit
\citep{triaud_spin-orbit_2010,hoyer_tramos_2013}.

>>>>

\tablecomments{
  (A) From TESS lightcurves (\S~\ref{sec:measurement}).
  (B) \citet{hoyer_tramos_2013}.
  (C) \citet{triaud_spin-orbit_2010}.
  (D) From HARPS spectra \citep{doyle_accurate_2013}.
  (E) \citet{stassun_accurate_2017}.
  (F) From functions of stellar, transit or RV parameters as discussed in text.
  (G) {\it Gaia} DR2.
  (H) \citet{stassun_TIC_2018}.
}

@@

We compute the bolometric flux using broadband magnitudes from
available all-sky catalogs, as follows: $G$ from {\it Gaia\/} DR2,
$B_T V_T$ from {\it Tycho-2}, $BVgri$ from {\it APASS}, $JHK_S$ from {\it
2MASS}, and the {\it WISE}~1--4 passbands, thus spanning the
wavelength range 0.4--22~$\mu$m.  Combining the implied angular radius
with the {\it Gaia} DR2 parallax, and adjusting for the parallax
offset \citep{stassun_evidence_2018}, we obtain the stellar radius.
For the stellar mass, we started with the $a/R_\star$ value found by
\citet{hoyer_tramos_2013} from 26 ground-based transits.  The implied
semi-major axis and stellar density follow \citep{seager_unique_2003}.
Combining the density and radius gives the stellar mass.  We get the
planet radius using our measured $R_{\rm p}/R_\star$.  Finally, for
the planet mass we use the observed RV semi-amplitude and inclination
angle from the transit
\citep{triaud_spin-orbit_2010,hoyer_tramos_2013}.
